Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-08-25 paper/paper.tex
cleaned IFN calling and figure creation
- Clean up and simplify IFN calling.

- Place figures from `monocle_analysis.ipynb`
  in separate directory

%%% start genotypes figure %%%
\begin{figure}
\begin{fullwidth}
{\centering
\includegraphics[width=0.9\linewidth]{figures/p_genotypes.pdf}
}
\caption{
Viral genotypes and infection outcomes in single cells.
}
\label{fig:genotypes}

\figsupp[Genotypes and infection outcomes plotted separately for IFN+ and IFN- cells.]
{This plot shows the same data as \FIG{genotypes}, but with cells separated into columns based on whether they are IFN- or IFN+.}
{\includegraphics[height=0.95\textheight]{figures/p_genotypes_by_ifn.pdf}}
\label{figsupp:genotypes_by_ifn}

\figdata{A CSV file giving the genotypes is in \texttt{figures/genotypes.csv}.}
\label{figdata:genotypes}

>>>>

%%% start genotypes figure %%%
\begin{figure}
\begin{fullwidth}
{\centering
\includegraphics[width=0.9\linewidth]{figures/single_cell_figures/p_genotypes.pdf}
}
\caption{
Viral genotypes and infection outcomes in single cells.
}
\label{fig:genotypes}

\figsupp[Genotypes and infection outcomes plotted separately for IFN+ and IFN- cells.]
{This plot shows the same data as \FIG{genotypes}, but with cells separated into columns based on whether they are IFN- or IFN+.}
{\includegraphics[height=0.95\textheight]{figures/single_cell_figures/p_genotypes_by_ifn.pdf}}
\label{figsupp:genotypes_by_ifn}

\figdata{A CSV file giving the genotypes is in \texttt{figures/single_cell_figures/genotypes.csv}.}
\label{figdata:genotypes}
